Microlensing as a possible probe of event-horizon structure in quasars

### 2017-09-15 paper1/ms.tex
editing

\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{figures/cc_forward.eps}
\caption{\label{fig:cc_forward} Mock lightcurve fitted with the
  correct source type and caustic.  The upper panel shows the mock
  data points, and running through them is a seven-parameter best fit:
  these being the crescent parameters $(R_p,R_n,a,b)$ and additionally
  the start and end times and the overall normalisation.  (Ideal
  lightcurves for the same crescent parameters appear above in
  Figures~\ref{fig:lightcurve_gauss}, \ref{fig:a_var},
  \ref{fig:lightcurve_crescent} and \ref{fig:char_points}.)  The curve
  has $\chi^2_{(244)}=243, P=0.32$ indicating a good fit.  (The
  subscript 244 refers to degrees of freedom: 251~points less
  7~parameters.)  The lower panel shows the posterior distributions
  for $r_{1/2}$ (solid histogram) and $R_n/R_p$ (dashed histogram).
  Vertical dashes mark the correct values.}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{figures/gc_forward.eps}
\caption{\label{fig:gc_forward} Like Figures~\ref{fig:cc_forward} and
  \ref{fig:cc_backward}, but showing the best fit to a Gaussian
  source.  The histogram shows the posterior distribution of $r_{1/2}$
  (there is no $R_n$).  It appears to show $r_{1/2}$ as accurately
  recovered, but is not to be trusted, because the fit has
  $\chi^2_{(247)}=344, P=3\times10^{-6}$ indicating rejection of the
  Gaussian source.  Looking closely, the curve is a little too shallow
  near $t=3$, and it is unable to fit the second sub-peak near $t=5$.}
\end{figure}

@@

In addition to the source parameters, the fitting procedure includes
three nuisance parameters, namely the brightness normalisation and the
start and end points on the path.  The latter two are equivalent to
considering the location of the caustic with respect to the starting
point and the velocity component of the source transverse to the
caustic (that is, $v_p$).  The orientation of the source track is
another nuisance parameter.  For a pure fold, changing the orientation
of the source track is equivalent to changing $v_p$ and the
orientation of the source (see Figure~\ref{fig:infinite_fold}).  Since
the latter two parameters are already accounted for, we do not include
the orientation as a separate parameter.  Since the caustic is not a
perfect fold, disregarding the orientation of the source track will
introduce some systematic error.

Figures \ref{fig:cc_forward}--\ref{fig:gc_forward} show the numerical
results.  Each of these figures shows the mock data (the same in all
three cases) along with best fits and the fitted values and
uncertainties on $r_{1/2}$ and (if applicable) $R_n/R_p$.

Figure \ref{fig:cc_forward} shows a test of the fitting procedure.
The computer compares the mock data to different template
lightcurves. The templates come from taking a crescent source along
the path CB in Figure~\ref{fig:magnification_map}, but with varied
crescent parameters and varied start and finish points.  As the figure
shows, the lightcurve can be fitted to within the noise, and the
parameters $r_{1/2}$ and $R_n/R_p$ can be recovered.

Figure \ref{fig:cc_backward} attempts a somewhat more realistic
situation.  The mock lightcurve is the same as before, but the
templates come from taking a crescent source along the path AB in
Figure~\ref{fig:magnification_map}.  That is, the mock data and the
templates come from crossings of different caustics.  This mimics the
unavoidable systematic error of not knowing the caustic exactly.  The
fit is slightly degraded, but still acceptable.  The parameters
$r_{1/2}$ and $R_n/R_p$ are still recovered.  The parameters $a/R_p$
and $b/R_p$ were not correctly recovered, which is understandable from
the track change.

>>>>

\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{figures/cc_forward.eps}
\caption{\label{fig:cc_forward} Mock lightcurve fitted with the
  correct source type and caustic.  The upper panel shows the mock
  data points, and running through them is a seven-parameter best fit:
  these being the crescent parameters $(R_p,R_n,a,b)$ and additionally
  the start and end times and the overall normalisation.  (Ideal
  lightcurves for the same crescent parameters appear above in
  Figures~\ref{fig:lightcurve_gauss}, \ref{fig:a_var},
  \ref{fig:lightcurve_crescent} and \ref{fig:char_points}.)  The curve
  has $\chi^2_{(244)}=243, P=0.32$ indicating a good fit.  (The
  subscript 244 refers to degrees of freedom: 251~points less
  7~parameters.)  The lower panel shows the posterior distributions
  for $r_{1/2}/v_p$ (solid histogram) and $R_n/R_p$ (dashed histogram).
  Vertical dashes mark the correct values.}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{figures/gc_forward.eps}
\caption{\label{fig:gc_forward} Like Figures~\ref{fig:cc_forward} and
  \ref{fig:cc_backward}, but showing the best fit to a Gaussian
  source.  The histogram shows the posterior distribution of $r_{1/2}/v_p$
  (there is no $R_n$).  It appears to show $r_{1/2}/v_p$ as accurately
  recovered, but is not to be trusted, because the fit has
  $\chi^2_{(247)}=344, P=3\times10^{-6}$ indicating rejection of the
  Gaussian source.  Looking closely, the curve is a little too shallow
  near $t=3$, and it is unable to fit the second sub-peak near $t=5$.}
\end{figure}

@@

In addition to the source parameters, the fitting procedure includes
three nuisance parameters, namely the brightness normalisation and the
start and end points on the path.  The latter two are equivalent to
considering the location of the caustic with respect to the starting
point and the velocity component of the source transverse to the
caustic (that is, $v_p$).  The orientation of the source track is
another nuisance parameter.  For an ideal fold, changing the
orientation of the source track is equivalent to changing $v_p$ and
the orientation of the source (see Figure~\ref{fig:infinite_fold}).
Since the latter two parameters are accounted for, we do not include
the orientation of the track as a separate parameter.  Since the
caustic is not an ideal fold, disregarding the orientation of the
source track can be expected to introduce some systematic error.

Figures \ref{fig:cc_forward}--\ref{fig:gc_forward} show the numerical
results.  Each of these figures shows the mock data (the same in all
three cases) along with best fits and the fitted values and
uncertainties on $r_{1/2}/v_p$ and (if applicable) $R_n/R_p$.

Figure \ref{fig:cc_forward} shows a test of the fitting procedure.
The computer compares the mock data to different template
lightcurves. The templates come from taking a crescent source along
the path CB in Figure~\ref{fig:magnification_map}, but with varied
crescent parameters and varied start and finish points.  As the figure
shows, the lightcurve can be fitted to within the noise, and the
parameters $r_{1/2}/v_p$ and $R_n/R_p$ can be recovered.

Figure \ref{fig:cc_backward} attempts a somewhat more realistic
situation.  The mock lightcurve is the same as before, but the
templates come from taking a crescent source along the path AB in
Figure~\ref{fig:magnification_map}.  That is, the mock data and the
templates come from crossings of different caustics.  This is intended
to mimic the systematic errors arising from not knowing the caustic
exactly.  As Figure~\ref{fig:cc_backward} shows, the fit is slightly
degraded, but still acceptable.  The parameters $r_{1/2}/v_p$ and
$R_n/R_p$ are still recovered.  The parameters $a/R_p$ and $b/R_p$
(not shown in the Figure) giving the orientation of the crescent were
not correctly recovered; but this is understandable, because the AB
and CB tracks have different orientations with respect to the caustics
crossed.  The slight degradation of the fit can be understood as
follows.  Although the caustics are clean folds, they have some
curvature, and moreover the curvature is not identical in the two
caustics used for the mock data and the template.
